Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-11-29 paper/snakemajoranas.tex
Descreased font size a bit
Added comment decorations for sections
Added some introduction to the analytics

\section{Introduction}
In order to create a stable platform for quantum computing, Majorana bound states are one of the contenders currently being pursued. Currently, most efforts to create pairs of Majorana's are based on hybrid NS structures, where a lengthy strip of semiconductor is interfaced with one, or two superconductor structures. Assuming the right parameters, the semiconductor becomes topological and Majorana bound states appear at the ends of the segment. In practice however, multiple problems arise making even the observation, let alone the manipulation of Majorana's difficult.

@@

\section{Analytical estimate}
\begin{align}
    S &= \left(
    \begin{array}{rr}
    r_{ll}&t_{rl}\\
    t_{lr}&r_{rr}\\
    \end{array}
    \right) =
    \left(
    \begin{array}{rr}
    \beta_+ & e^{-i q W} \beta_-\\
    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
    \end{array}
    \right) 
    \\
    \beta_\pm &= \left(
    \begin{array}{rr}
    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
    \end{array}
    \right)\\
    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
\end{align}

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{\pm}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}

\begin{align}
    q &= \sqrt{\frac{2 m_\ast}{\hbar ^2}\left(\mu_s + E\right) - k_x^2}\\
    k_1 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }\\
    k_2 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }
\end{align}
\section{Numerical bandstructures}

@@

\section{Calculating the bandstuctures.}

\section{Calculating the topological phase diagram.}

@@

\section{Localization lengths and shape effect}

@@

\section{Discussion and Conclusions}

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
In order to create a stable platform for quantum computing, Majorana bound states are one of the contenders currently being pursued. Currently, most efforts to create pairs of Majorana's are based on hybrid NS structures, where a lengthy strip of semiconductor is interfaced with one, or two superconductor structures. Assuming the right parameters, the semiconductor becomes topological and Majorana bound states appear at the ends of the segment. In practice however, multiple problems arise making even the observation, let alone the manipulation of Majorana's difficult.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate}
We claim that the hardening of the gap is due to the cutoff of long trajectories. 
In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
We then compute the scattering matrix to find the Andreev bound spectrum as a function of the momentum along the strip direction.
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

\begin{align}
    S &= \left(
    \begin{array}{rr}
    r_{ll}&t_{rl}\\
    t_{lr}&r_{rr}\\
    \end{array}
    \right) =
    \left(
    \begin{array}{rr}
    \beta_+ & e^{-i q W} \beta_-\\
    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
    \end{array}
    \right) 
    \\
    \beta_\pm &= \left(
    \begin{array}{rr}
    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
    \end{array}
    \right)\\
    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
\end{align}

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}
\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\end{align}
\end{footnotesize}

%%██████████████████████████████████████████████████████████████████████████
%%██ Numerical bandstructures
%%██████████████████████████████████████████████████████████████████████████
\section{Numerical bandstructures}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the topological phase diagram
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the topological phase diagram.}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effect}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Discussion and Conclusions
%%██████████████████████████████████████████████████████████████████████████
\section{Discussion and Conclusions}
